\stdpopsim: a community-maintained standard library of population genetic simulations

### 2019-12-16 popSimManu.tex
cleaned minor typos

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.5\linewidth]{display_items/Figure1.png}
\caption{\textbf{Structure of \stdpopsim}. \textbf{A.} The
hierarchical organization of the PopSim catalog contains all information
within individual species. Information within the species level is shown here
for \emph{Homo sapiens} only. We see that \emph{H. sapiens} is associated
with a default generation time and mutation rate, that it contains within
it a representation of the physical genome, genetic maps, and as shown a
subset of the demographic models currently implemented. \textbf{B.} Caching
and automated download of genetic maps. \textbf{C.} Example code to specify
and simulate models using \stdpopsim via the API (top) or
command-line interface (bottom). \textbf{D.} Simulation output from
\stdpopsim is generated as tree sequence files that can
be manipulated and analysed with \texttt{tskit}.}
\label{fig:cartoon}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/homo_sapiens_mask_Ragsdale.png}
\caption{\textbf{Comparing estimates of $N(t)$ in humans}. Here we show estimates of population
size over time ($N(t)$) inferred using 4 different methods, \smcpp, \texttt{stairwayplot},
\MSMC with $n=2$ and $n=8$. Data were generated by simulating
replicate human genomes under the \cite{ragsdale2019models} model and using the
HapMapII genetic map~\citep{international2007second}. From top to bottom we show estimates for each
of the three populations in the model YRI, CEU, and CHB. In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:n_t_ragsdale}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/d_mel_Sheehan_mask2.png}
\caption{\textbf{Comparing estimates of $N(t)$ in \emph{Drosophila}}. Population
size over time ($N(t)$) estimated from an African population sample. Data were generated by simulating
replicate \emph{D.melanogaster} genomes under the three-epoch \cite{sheehan2016deep} model
with the genetic map inferred in \cite{comeron2012many}. In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:n_t_sheehan}
\end{center}
\end{figure}

@@

Our goal for the two population analysis pipeline was to explore two population inference
on some of the multi-population demographic models implemented in \stdpopsim.
For HomSap we examined the OutOfAfrica_3G09 model with the HapmapII\_GRCh37 genetic map,
and for DroMel we simulated under the OutOfAfrica_2L06 model with the Comeron2012\_dm6.
The HomSap model is a three population model (Africa, Europe, and Asia) including post-divergence
migration and exponential growth (Figure \ref{fig:IM_popn_human}C), whereas the
DroMel model is a two population model (Africa and Europe) with no post-divergence
migration and constant population sizes (Figure \ref{fig:two_popn_fly}).

@@

From HomSap we ran replicate whole genome simulations under the model
and specified taking 20 samples each from the Europe and Africa populations. 
For DroMel, runtimes under OutOfAfrica_2L06 were prohibitively slow for
running whole genome simulations. Instead we simulated 3 Mb of chromosome 2R.
and take 50 samples from each of
the Africa and Europe populations. We tried to run whole genome simulations under
this model but after XXXX amount of time... (JRA fill in details here). For the generic
IM simulations, we used the HomSap genome along with the HapmapII\_GRCh37 genetic map,
and sampled 20 individuals from each population.

@@

\pagebreak
\beginsupplement
\section*{Supplemental Figures}
\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/homo_sapiens_mask_Gutenkunst.png}
\caption{\textbf{Comparing estimates of $N(t)$ in humans}. Here we show estimates of population
size over time ($N(t)$) inferred using 4 different methods, \smcpp, \stairwayplot,
\MSMC with $n=2$ and $n=8$. Data were generated by simulating
replicate human genomes under the \cite{gutenkunst2009inferring} model and using the genetic map
inferred in \cite{international2007second}. From top to bottom we show estimates for each
of the three populations in the model YRI, CEU, and CHB. In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:n_t_gutenkunst}
\end{center}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.5\linewidth]{display_items/Figure1.pdf}
\caption{\textbf{Structure of \stdpopsim}. \textbf{A.} The
hierarchical organization of the PopSim catalog contains all information
within individual species. Information within the species level is shown here
for \emph{Homo sapiens} only. We see that \emph{H. sapiens} is associated
with a default generation time and mutation rate, that it contains within
it a representation of the physical genome, genetic maps, and as shown a
subset of the demographic models currently implemented. \textbf{B.} Caching
and automated download of genetic maps. \textbf{C.} Example code to specify
and simulate models using \stdpopsim via the API (top) or
command-line interface (bottom). \textbf{D.} Simulation output from
\stdpopsim is generated as tree sequence files that can
be manipulated and analysed with \texttt{tskit}.}
\label{fig:cartoon}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/homo_sapiens_mask_Ragsdale.pdf}
\caption{\textbf{Comparing estimates of $N(t)$ in humans}. Here we show estimates of population
size over time ($N(t)$) inferred using 4 different methods, \smcpp, \texttt{stairwayplot},
\MSMC with $n=2$ and $n=8$. Data were generated by simulating
replicate human genomes under the \cite{ragsdale2019models} model and using the
HapMapII genetic map~\citep{international2007second}. From top to bottom we show estimates for each
of the three populations in the model YRI, CEU, and CHB. In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:n_t_ragsdale}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/d_mel_Sheehan_mask2.pdf}
\caption{\textbf{Comparing estimates of $N(t)$ in \emph{Drosophila}}. Population
size over time ($N(t)$) estimated from an African population sample. Data were generated by simulating
replicate \emph{D.melanogaster} genomes under the three-epoch \cite{sheehan2016deep} model
with the genetic map inferred in \cite{comeron2012many}. In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:n_t_sheehan}
\end{center}
\end{figure}

@@

Our goal for the two population analysis pipeline was to explore two population inference
on some of the multi-population demographic models implemented in \stdpopsim.
For HomSap we examined the OutOfAfrica\_3G09 model with the HapmapII\_GRCh37 genetic map,
and for DroMel we simulated under the OutOfAfrica\_2L06 model with the Comeron2012\_dm6.
The HomSap model is a three population model (Africa, Europe, and Asia) including post-divergence
migration and exponential growth (Figure \ref{fig:IM_popn_human}C), whereas the
DroMel model is a two population model (Africa and Europe) with no post-divergence
migration and constant population sizes (Figure \ref{fig:two_popn_fly}).

@@

From HomSap we ran replicate whole genome simulations under the model
and specified taking 20 samples each from the Europe and Africa populations. 
For DroMel, runtimes under OutOfAfrica\_2L06 were prohibitively slow for
running whole genome simulations. Instead we simulated 3 Mb of chromosome 2R.
and take 50 samples from each of
the Africa and Europe populations. We tried to run whole genome simulations under
this model but after XXXX amount of time... (JRA fill in details here). For the generic
IM simulations, we used the HomSap genome along with the HapmapII\_GRCh37 genetic map,
and sampled 20 individuals from each population.

@@

\pagebreak
\beginsupplement
\section*{Supplemental Figures}
\begin{figure}
\begin{center}
\includegraphics[width=0.8\linewidth]{display_items/homo_sapiens_mask_Gutenkunst.pdf}
\caption{\textbf{Comparing estimates of $N(t)$ in humans}. Here we show estimates of population
size over time ($N(t)$) inferred using 4 different methods, \smcpp, \stairwayplot,
\MSMC with $n=2$ and $n=8$. Data were generated by simulating
replicate human genomes under the \cite{gutenkunst2009inferring} model and using the genetic map
inferred in \cite{international2007second}. From top to bottom we show estimates for each
of the three populations in the model YRI, CEU, and CHB. In shades of blue we show the estimated
$N(t)$ trajectories for each replicate. In black we show the true population size history as inferred
for the rate of coalescence in the demographic model.}
\label{fig:n_t_gutenkunst}
\end{center}
\end{figure}
